### 2019-10-09 paper/results.tex
Osama's comments impelemented

Opposite observation has been made for the Pu reactor-grade and TRU cases. For 
these cases, the thermal neutron flux is increasing during operation while 
fast neutron flux is decreasing. Fissile plutonium nuclides (generate 
relatively hard spectrum) from initial fuel salt composition is gradually 
substituted with the $^{233}$U (generates relatively soft spectrum), produced 
from the fertile $^{232}$Th. During reactor operation, the $^{233}$U becomes 
primary fissile isotope, which leads to the neutron spectrum softening of the 
reactor. 
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_thermal_flux_init_vs_eq.png} 
	\caption{Radial thermal neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium for initial and 
		equilibrium fuel salt composition (the thermal flux confidence 
		interval 
		$\pm\sigma<1.6$\% for all cases).}
	\label{fig:thermal_flux}
\end{figure}

Notably, more changes in thermal neutron flux shape and magnitude for  
$^{233}$U case were observed in the inner core zone ($R\lesssim150$) than 
in the outer core zone. In contrast, for Pu reactor-grade and TRU cases, 
significant changes were observed for thermal neutron flux in the outer core 
zone and reflector. Additionally, Figure~\ref{fig:thermal_flux} shows 
relatively large changes in thermal flux leakage from the core for the Pu and 
TRU cases. Overall, the SD-TMSR core design was optimized for $^{233}$U 
fissile isotope \cite{li_optimization_2018}; hence, the core geometry (e.g., 
fuel channels lattice pitch) must be re-optimized for another type of fuel to 
obtain better neutronics performance.

\subsection{Temperature coefficient of reactivity}
The temperature coefficient of reactivity quantifies reactivity changes due to 
temperature increase in the core and was calculated in this work as follows:
\begin{align}
\alpha &= \frac{k_{eff}(T_{i+1}) - k_{eff}(T_i)}{k_{eff}(T_{i+1}) 
	k_{eff}(T_{i}) (T_{i+1} - T_i)}
\intertext{where}
k_{eff} &= \mbox{effective multiplication factor} \nonumber \\
T_i &= \mbox{fuel salt temperature in (900K, 1000K).} \nonumber
\end{align}

@@

The \gls{MTC} for the $^{233}$U case is positive and decreases during reactor 
operation because of spectrum hardening with fuel depletion. For other cases, 
the \gls{MTC} is negative and also decreasing in magnitude during the reactor 
operation. Finally, the total temperature coefficient of reactivity is 
strongly negative for all considered scenarios but decreases in magnitude 
during reactor operation due to spectral shift. Notably, the total temperature 
coefficient is the most negative for the Pu reactor-grade case at startup, 
which has the hardest neutron spectrum (Figure~\ref{fig:spectrumFLUX110vC}). 
These coefficients agree with earlier estimates for SD-TMSR 
\cite{li_optimization_2018,Ashraf2019Whole} and \gls{MSBR} 
\cite{rykhlevskii2019modeling, 
rykhlevskii_full-core_2017,robertson_conceptual_1971}.

@@

Table~\ref{tab:six_factor} summarizes the six factors for 3 different initial 
fuel salt compositions at startup and equilibrium. Using SERPENT-2 built-in 
online reprocessing capabilities, all six factors have been calculated at the 
beginning of the operation and after 30 years of operation. Neutron population 
and number of active/inactive cycles were selected to obtain $k_{eff}$ 
statistical uncertainty less than 12 pcm. The fast and thermal non-leakage 
probabilities  remain constant regardless of initial fissile material and 
neutron spectrum shift during operation. The thermal utilization factor (f) 
remains almost constant during operation for $^{233}$U and TRU cases but 
considerably declines for Pu case due to significant neutron spectrum 
softening.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [ht!]
	\caption{Six factors for the SD-TMSR model for 3 different initial 
		fuel salt compositions at startup and equilibrium.}
	\begin{tabularx}{\textwidth}{ X | X X  X X  X X } \hline
		\multirow{3}{*}{Factor}  & \multicolumn{6}{c}{Startup fissile 
			material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil & Initial & Equil & Initial & Equil \\ \hline
		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.59 & 1.31 \\ 
		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75 \\
		p       & 0.54 & 0.43 & 0.26 & 0.16 & 0.17 & 0.15 \\
		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81 \\
		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99 \\
		P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ \hline
	\end{tabularx}
	\label{tab:six_factor}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Opposite behavior was observed for the Pu reactor-grade and TRU cases. For 
these cases, the thermal neutron flux is increasing during operation while 
fast neutron flux is decreasing. Fissile plutonium nuclides (generate 
relatively hard spectrum) from initial fuel salt composition is gradually 
substituted with the $^{233}$U (generates relatively soft spectrum), produced 
from the fertile $^{232}$Th. During reactor operation, the $^{233}$U becomes 
primary fissile isotope, which leads to the neutron spectrum softening of the 
reactor. 
\begin{figure}[htp!] % replace 't' with 'b' to force it to \centering
	\includegraphics[width=\textwidth]{radial_thermal_flux_init_vs_eq.png} 
	\caption{Radial thermal neutron flux distribution for 3 different initial 
		fuel salt compositions at startup and equilibrium (the thermal flux 
		confidence interval $\pm\sigma<1.6$\% for all cases).}
	\label{fig:thermal_flux}
\end{figure}

Notably, more changes in thermal neutron flux shape and magnitude for  
$^{233}$U case were observed in the inner core zone ($R\lesssim150$) than 
in the outer core zone. In contrast, for Pu reactor-grade and TRU cases, 
significant changes were observed for thermal neutron flux in the outer core 
zone and reflector. Additionally, Figure~\ref{fig:thermal_flux} shows 
relatively large changes in thermal flux leakage from the core for the Pu and 
TRU cases. Overall, the SD-TMSR core design was optimized for $^{233}$U 
fissile isotope \cite{li_optimization_2018}; thus, the core geometry (e.g., 
fuel channels lattice pitch) must be re-optimized for another type of fuel to 
obtain better neutronics performance.

\subsection{Temperature coefficient of reactivity}
The temperature coefficient of reactivity quantifies reactivity changes due to 
temperature increase in the core and was calculated in this work as follows:
\begin{align}
\alpha &= \frac{k_{eff}(T_{i+1}) - k_{eff}(T_i)}{k_{eff}(T_{i+1}) 
	k_{eff}(T_{i}) (T_{i+1} - T_i)}
\intertext{where}
k_{eff} &= \mbox{effective multiplication factor} \nonumber \\
T_i &= \mbox{fuel salt temperature in (900 K, 1000 K).} \nonumber
\end{align}

@@

The \gls{MTC} for the $^{233}$U case is positive and decreases during reactor 
operation because of spectrum hardening with fuel depletion. For other cases, 
the \gls{MTC} is negative and also decreasing in magnitude during the reactor 
operation. Finally, the total temperature coefficient of reactivity is 
strongly negative for all considered scenarios but decreases in magnitude 
during reactor operation due to spectral shift. Notably, the total temperature 
coefficient is the most negative for the Pu reactor-grade case at startup, 
which has the hardest neutron spectrum (Figure~\ref{fig:spectrumFLUX110vC}). 
These coefficients agree with earlier estimates for SD-TMSR 
\cite{li_optimization_2018, ashraf2019whole_core} and \gls{MSBR} 
\cite{rykhlevskii2019modeling,  
rykhlevskii_full-core_2017,robertson_conceptual_1971}.

@@

Table~\ref{tab:six_factor} summarizes the six factors for 3 different initial 
fuel salt compositions at startup and equilibrium. By using SERPENT-2 built-in 
online reprocessing capabilities, all six factors have been calculated at the 
beginning of the operation and after 30 years of operation. Neutron population 
and number of active/inactive cycles were selected to obtain $k_{eff}$ 
statistical uncertainty less than 12 pcm. The fast and thermal non-leakage 
probabilities  remain constant regardless of initial fissile material and 
neutron spectrum shift during operation. The thermal utilization factor (f) 
remains almost constant during operation for $^{233}$U and TRU cases but 
considerably declines for Pu case due to significant neutron spectrum 
softening.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table} [ht!]
	\caption{Six factors for the SD-TMSR model for 3 different initial 
		fuel salt compositions at startup and equilibrium.}
	\begin{tabularx}{\textwidth}{ X | X X  X X  X X } \hline
		\multirow{3}{*}{Factor}  & \multicolumn{6}{c}{Startup fissile 
			material} \\ \cline{2-7}
		\space  & \multicolumn{2}{c}{$^{233}U$} & \multicolumn{2}{c}{Pu} & 
		\multicolumn{2}{c}{TRU} \\ \cline{2-7}
		\space  & Initial & Equil & Initial & Equil & Initial & Equil \\ \hline
		$\eta$  & 1.26 & 1.40 & 1.66 & 1.44 & 1.59 & 1.31 \\ 
		f       & 0.97 & 0.98 & 0.96 & 0.76 & 0.80 & 0.75 \\
		p       & 0.54 & 0.43 & 0.26 & 0.16 & 0.17 & 0.15 \\
		$\epsilon$ & 1.49 & 1.67 & 2.45 & 5.87 & 4.83 & 6.81 \\
		P$_f$   & 0.99 & 0.99 & 0.99 & 0.99& 0.99 & 0.99 \\
		P$_t$   & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\ \hline
	\end{tabularx}
	\label{tab:six_factor}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
